Higher-Order unification for free!

### 2024-04-16 paper/main.tex
clean proof lemma 5.14

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetaright is between
  terms in \wellb.
  \label{lemma:unif-eta-2}
\end{lemma}

\begin{proof}[Proof sketch]
  \lhs is variable, and, by \cref{def:progressetaright}, \rhs is either no more
  a \maybeeta, i.e. \rhs is not a $\eta$-expansion and, so, $\wellb(\rhs)$,
  otherwise, \rhs can reduce to a term which cannot be a $\eta$-expansion, and,
  so, $\wellb(\rhs)$. In both cases, the unification between \rhs and \lhs
  is done between terms that are in \wellb.
\end{proof}

>>>>

\begin{lemma}
  Given a \linketa \linketaM{\Gamma}{X}{\lambda x.t}, the unification done by \progressetaright is between
  terms in \wellb.
  \label{lemma:unif-eta-2}
\end{lemma}

\begin{proof}[Proof sketch]
  $X$ is variable, and, by \cref{def:progressetaright}, $\lambda x.t$ is either no more
  a \maybeeta, i.e. it is not a $\eta$-expansion and, so, $\wellb(\lambda x.t)$, 
  the unification is performed between $X$ and $\lambda x.t$.
  Otherwise, $\lambda x.t$ has the shape $\lambda x.t' \appsep x$ with $x$ not free in $t'$ and
   $\wellb(t')$. In this second case the unification is done between $X$ and $t'$.
  In both cases, unifications are between \wellb terms.
\end{proof}
